Interactive plot for exploring results of Gaussian mean estimation experiments

### 2018-12-06 shiny/gauss_shiny.Rmd
I have an initial setup of the Shiny server document.

---
title: "Graphs"
runtime: shiny
output: html_document
---

NOTE: To launch the Shiny app, run `rmarkdown::run("shiny.Rmd")`

@@

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
load("../output/dscr.RData")
scenario_names = as.character(unique(res$scenario))
method_names = as.character(unique(res$method))

@@

    # Create the checkboxes and select them all by default
    checkboxGroupInput("scen.subset", "Choose Scenarios", 
                        choices  = scenario_names,
                        selected = "sp.1.v2"),

>>>>

---
title: "Interactive plot for exploring results of Gaussian mean estimation experiments"
runtime: shiny
output: html_document
---

*Briefly explain here what this R Markdown document is for.*

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE)
```

```{r load-pkgs, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(rmarkdown)
```

Load results
------------

Load the results of the simulation experiments.

```{r load-results}
load("../output/dscr.RData")
```

@@

```{r, echo=FALSE}
scenario_names = as.character(unique(res$scenario))
method_names = as.character(unique(res$method))

@@

    # Create the checkboxes and select them all by default.
    checkboxGroupInput("scen.subset", "Choose Scenarios", 
                        choices  = scenario_names,
                        selected = "sp.1.v2"),
